|

### 2022-07-14 paper/paper.Rmd
reference ggplot2 and ggally
mapping out discussion

@@

# Experimenting with new techniques using Mathematica {#sec:implementation}

@@

# Extension added in the R package `tourr`

@@

# What would be desirable for implementations in R?

@@

@@

The authors gratefully acknowledge the support of the Australian Research Council. The paper was written in `rmarkdown` [@rmarkdown] using `knitr` [@knitr].

@@

>>>>

XXX Equation for arbitrary center for slice; and move the "the implementation ..." into the software section once that is constructed; and "potential adjustments for future" into the section on desirable controls

@@

@@

# Software {#sec:implementation}

## Mathematica notebook

## Extensions to the R package `tourr`

@@

Changing slice center

## Desirable interactivity

@@

Recap contribution

Where else might it be useful to use mathematica

@@

The authors gratefully acknowledge the support of the Australian Research Council. The paper was written in `rmarkdown` [@rmarkdown] using `knitr` [@knitr]. The scatterplot matrix of the penguins data was produced by the GGally [@GGally] package built on ggplot2 [@ggplot2] graphics.

@@

Mathematica notebook

Appendix
